\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
     \usepackage[nonatbib]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{The Effect of Neuron Selection on Policy Generalization}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Timothy J. Whitaker\\
  Department of Computer Science\\
  Colorado State University\\
  Fort Collins, CO 80525 \\
  \texttt{timothy.whitaker@colostate.edu} \\
  % examples of more authors
  % \And
  % Darrell Whitley \\
  % Colorado State University\\
  % Fort Collins, CO 80525 \\
  % \texttt{darrell.whitley@colostate.edu} \\
  % \And
  % Dave Matthews \\
  % Colorado State University\\
  % Fort Collins, CO 80525 \\
  % \texttt{dave.matthews@colostate.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Introduction}

\section{Methods}

We experiment with 7 different state of the art reinforcement learning algorithms. These are: Advantage Actor Critic (A2C), Actor Critic using Kronecker Factored Trust Region (ACKTR), Deep Deterministic Policy Gradient (DDPG), Proximal Policy Optimization (PPO), Soft Actor Critic (SAC), Twin Delayed Deep Deterministic Policy Gradient (TD3), and Trust Region Policy Optimization (TRPO). Model implementations are provided by the open source library Stable Baselines[https://github.com/hill-a/stable-baselines].

We experiment with two versions of each model. One with default hyperparameters given by the paper authors and one with hyperparameters tuned to each environment.

\subsection{Training}

Each model is trained from only a single initial state.

We implement two training methodologies.

1. We train each model for a globally fixed number of timesteps.
2. We train each model until they have "solved" the environment.


\section{Results}

\subsection{Markovian Tasks}
\subsubsection{Single Pole Cart Balancing}
\subsubsection{Double Pole Cart Balancing}

\subsection{Non-Markovian Tasks}
\subsubsection{Single Pole Cart Balancing}
\subsubsection{Double Pole Cart Balancing}

\section*{References}

\section{Hyperparameters}

Advantage Actor Critic (A2C)
Actor Critic using Kronecker Factored Trust Region (ACKTR)
Deep Deterministic Policy Gradient (DDPG)
Proximal Policy Optimization (PPO)
Soft Actor Critic (SAC)
Twin Delayed Deep Deterministic Policy Gradient (TD3)
Trust Region Policy Optimization (TRPO)

\end{document}
